NMRlipids Databank makes data-driven analysis of biomembrane properties accessible for all

### 2023-02-28 main.tex
UPdate text

Divergent predictions for the lateral packing of POPC and POPE membranes from different force fields is illustrated in Fig.~\ref{fig:POPCPOPEapls}C. To select the best models for these membranes, the ranking based on C--H bond order parameter quality for the best performing POPC and POPE simulations in the NMRlipids databank are shown in Figs.~\ref{fig:quality}A and B, respectively. Direct comparisons with the experimental are shown in Figs.~\ref{fig:quality}C--E and~\ref{fig:POPC_POPE_dataSI} for the most relevant simulations. Based on these rankings, simulations with Slipids parameters are the most realistic for POPC lipids with a clear difference to others, and 2\textsuperscript{nd} most realistic for POPE with only marginally lower quality than GROMOS-CKP simulations. Simulations with CHARMM36 and GROMOS-CKP parameters predict overly packed bilayer for POPC (overestimated order in Fig.~\ref{fig:POPC_POPE_dataSI}), while the area per lipid for POPC is overestimated in Lipid17. For POPE, CHARMM36 and Lipid17 predict membranes that are too packed. 
Because the area per lipid correlates with the average order parameter of the $\textit{sn}$-1 chain (Fig.~\ref{fig:quality} F), quality evaluation in Fig.~\ref{fig:quality} and direct comparison in Fig.~\ref{fig:POPC_POPE_dataSI} can be used to select the simulations that best capture area per lipids for POPE and POPC lipids in Fig.~\ref{fig:POPCPOPEapls}C.
In conclusion, the quality evalution based on the NMRlipids databank suggests that Slipids parameters are the best available choice for simulations with PC and PE lipids, at least for the cases were membrane packing is relevant.

>>>>

Divergent predictions for the lateral packing of POPC and POPE membranes from different force fields is illustrated in Fig.~\ref{fig:POPCPOPEapls}C. Because the membrane packing in terms of area per lipid correlates with the average order parameter of the $\textit{sn}$-1 chain (Fig.~\ref{fig:quality} F), simulations with the best quality for this part of POPE and POPC lipids are considered to give the most realistic results in Fig.~\ref{fig:POPCPOPEapls}C. To this end, the ranking based on C--H bond order parameter quality for the best performing POPC and POPE simulations in the NMRlipids databank are shown in Figs.~\ref{fig:quality}A and B, respectively. Direct comparisons with the experimental data are shown in Figs.~\ref{fig:quality}C--E and~\ref{fig:POPC_POPE_dataSI} for the most relevant simulations. Based on these rankings, simulations with Slipids parameters are the most realistic for POPC lipids with a clear difference to others, and 2\textsuperscript{nd} most realistic for POPE with only marginally lower quality than GROMOS-CKP simulations. Simulations with CHARMM36 and GROMOS-CKP parameters predict overly packed bilayer for POPC (overestimated order in Fig.~\ref{fig:POPC_POPE_dataSI}), while the area per lipid for POPC is overestimated in Lipid17. For POPE, CHARMM36 and Lipid17 predict membranes that are too packed. In conclusion, the quality evalution based on the NMRlipids databank suggests that Slipids parameters are the best available choice for simulations with PC and PE lipids, at least for the cases were membrane packing is relevant.
